An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-29 draft.tex
Justifying containers

\item Each population is then pushed to the \texttt{Input} queue, so they can be consumed 
by Stateless functions responsible for the execution of the search.  % Why the caps in Stateless? - JJ  
% It refers to the swimlines in the diagram, maybe I should point it out  - Mario
% Added a comment above. - Mario

@@

In contrast, in the classic Island model shown in Figure
\ref{fig:classicisland}, algorithms are coupled with a population, and the same processing
node keeps both the algorithm process and the state of the population.  Other
processing nodes follow the same configuration and form of execution, and they
only pass specific individuals between them.  In this model, adding additional
processing nodes, on-runtime, can be more difficult, because they need to have
an addressing mechanism. % JJ, help I don't know if this is clearly understood, a mean like a DNS - Mario

@@

We have mentioned several advantages of a cloud-native application for running
multi-population based algorithms, but there are in our experience several
practical issues of this approach. In general, cloud platforms have free-tiers
for their services, and many offer academic discounts to students. But once we
pass to the pay-as-you-go tier, computing resources need to be
managed, and, where possible, its cost minimized.  First,
in many cases,  a credit-card is needed to guarantee the payment of the
resources consumed and someone responsible for assigning quotas and, more
importantly, special keys for using the cloud's API.  If these keys are
compromised or shared by their holders,  additional costs or administrative
procedures are in order. For those cases when a prototype platform is needed,
for instance, students developing a new algorithm variant or experimenting with
a published work, a container-based platform can be more practical. Container
technology enables researchers the local deployment of all the infrastructure
needed to run the experiments. Later, if needed, the same deployment could be
deployed to the cloud.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario

>>>>

\item Each population is then pushed to the \texttt{Input} queue, so they can be consumed 
by Stateless functions responsible for the execution of the search.

@@

In contrast, in the classic Island model shown in Figure
\ref{fig:classicisland}, algorithms are  population methods, and the same processing
node keeps both the algorithm process and the state of the population.  Other
processing nodes follow the same configuration and form of execution, and they
only pass specific individuals between them.  In this model, adding additional
processing nodes, on-runtime, can be more difficult, because they need to have
an addressing mechanism or simply be aware of these new nodes. This is
solved in part in Peer to Peer (P2P) evolutionary algorithms
\cite{juanlu:europar}, but coupling still exists, meaning that every
node must run the whole evolutionary algorithm and hold full copies of
its subpopulation. 
% JJ, help I don't know if this is clearly understood, a mean like a
% DNS - Mario
% Added something - JJ

@@

We have mentioned several advantages of a cloud-native application for running
multi-population based algorithms, but there are in our experience several
practical issues of this approach. In general, cloud platforms have free-tiers
for their services, and many offer academic discounts to students. But once we
pass to the pay-as-you-go tier, computing resources need to be
managed, and, where possible, its cost minimized.  First,
in many cases,  a credit-card is needed to guarantee the payment of the
resources consumed and someone responsible for assigning quotas and, more
importantly, special keys for using the cloud's API.  If these keys are
compromised or shared by their holders,  additional costs or administrative
procedures are in order. For those cases when a prototype platform is needed,
for instance, students developing a new algorithm variant or experimenting with
a published work, a container-based platform can be more practical. Container
technology enables researchers the local deployment of all the infrastructure
needed to run the experiments. Later, if needed, the same system could be
deployed to the cloud.

The main advantage of container deployments over virtual machine
instances is that they add much less overhead to communication between
them, and they are much more economical to deploy. Scaling and
monitoring can be done much more easily through cloud orchestration
systems such as Kubernetes; these are the reasons why we chose it for
this work.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario
